--- 

title: "Analisi factores asociados al mercado inmobiliario"
author: "Juan Luis Castillo"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "aqui va algo, todavia de momento no sepo"
---


````{r libreria, message=FALSE,warning=FALSE }
library(tidyverse)
library(dplyr)

````

```{r data}
data<-read.csv("data/housing.csv")

```
```{r}
head(data,n=5)
```


````{r estrcutura}
str(data)

````



````{r faltantes}
data %>% 
   summarise(across(everything(),~ sum(is.na(.)),.names="NA_{.col}"))

````

```{r}
data %>% 
  mutate(across(
    where(is.numeric),
    ~ ifelse(is.na(.),mean(.,na.rm=TRUE),.)
  )) -> df
```
verifiquemos si tiene datos faltantes
```{r faltante2}
df %>% 
   summarise(across(everything(),~ sum(is.na(.)),.names="NA_{.col}"))

```

```{r factorocean}
df$ocean_proximity <- factor(df$ocean_proximity)
```
```{r}
df %>%  summarise (n=length(median_house_value),
                            media=mean(median_house_value),
                            sd=sd(median_house_value),
                            mediana=median(median_house_value),
                            RIC=IQR(median_house_value),
                            q1=quantile(median_house_value,0.25),
                            q3=quantile(median_house_value,0.75),
                            minimo=min(median_house_value),
                            maximo=max(median_house_value)
                            
                            
                            ) 
```
 
 Hay un numero total de 20640 casas en la zona de California. Las cuales poseen un valor medio individual de 206855.8 USD, este valor medio presenta una desviacion estandar de cerca de 115395.6 USD. 
 El 50% de el valor de las casas es igual o menor a 179700 USD. El valor mas bajo listado de 14999 dolares, siendo el precio mayor de cerca de 500001 dolares. El 25% de los valores es menor igual a 119600 dolares, y hasta el 75% de los precios listados llegan hasta los 264725.
 
```{r}
df %>% 
  ggplot(aes(x=median_house_value))+
  geom_histogram(aes(y=after_stat(density)),
                 binwith=2500,
                 fill="#0af1f5",
                 color="white",
                 alpha=0.6)+
      geom_density(color="darkblue",linewidth=1.2)+labs(title='Distribucion del valor medio de las viviendas',
  x='valor medio de la casa(USD)',
  y='densidad')+
        theme()
                                                        
                                                        )
  
                 
  
```
 
 
```{r}
df %>% 
  ggplot(aes(y="",x=median_house_value))+
  geom_boxplot(fill="#0af1f5",color="black",outlier.color = "darkred")+
  stat_summary(fun=mean,geom='point',shape=20)+
  theme_bw()

  
  
```
 
 ## Analisis de las variables independientes (caracteristicas)
 
```{r}
df %>% 
  select(where(is.numeric),-median_house_value) %>% 
  pivot_longer(
    cols=everything(),
    names_to = 'variable',
    values_to = 'valor',
    
  ) %>% 
  group_by(variable) %>% 
  summarise (n=length(valor),
                            media=mean(valor),
                            sd=sd(valor),
                            mediana=median(valor),
                            RIC=IQR(valor),
                            q1=quantile(valor,0.25),
                            q3=quantile(valor,0.75),
                            minimo=min(valor),
                            maximo=max(valor)) 
  


```
```{r}
tabla_ocean_b <- df %>%
  count(ocean_proximity,name="n") %>%
  mutate(Porcentaje=round((n/sum(n))*100,1),
         Etiqueta=paste0(n,"(",Porcentaje,"%)"))


tabla_ocean_b %>%
  ggplot(aes(x=ocean_proximity,y=n))+
  geom_col(fill="lightgreen",width = 0.6)+
  geom_text(aes(label=Etiqueta),vjust = 0.6,size = 4.5)+
  facet_wrap(~'Distribucion de la variable ocean proximity')+
  scale_y_continuous(expand = expansion(mult =c(0,0.15)))+
  theme_bw()
  
```

```{r valoresingreso}
df %>%
  ggplot(aes(x=median_income,y=median_house_value))
  geom_point(alpha = 0.4,color='darblue')+
    labs(y='Valor medio de la vivienda',
         x='ingreso medio')+
    
    

```

 
 ahora comparamos el valor medio de la vivienda segun 

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

Math can be added in body using usual syntax like this 

## math example

$p$ is unknown but expected to be around 1/3. Standard error will be approximated

$$
SE = \sqrt{\frac{p(1-p)}{n}} \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
$$

You can also use math in footnotes like this^[where we mention $p = \frac{a}{b}$].

We will approximate standard error to 0.027[^longnote]

[^longnote]: $p$ is unknown but expected to be around 1/3. Standard error will be approximated

    $$
    SE = \sqrt{\frac{p(1-p)}{n}} \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
    $$

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

